\documentclass[12pts]{article}
\begin{document}
\title{AI used to underatnd facts about the topic and bring that topics from "pseudoscience" to "science" }
\maketitle
Criticism of pseudoscience, generally by the scientific community or skeptical organizations, involves critiques of the logical, methodological, or rhetorical bases of the topic in question. Though some of the listed topics continue to be investigated scientifically, others were only subject to scientific research in the past and today are considered refuted, but resurrected in a pseudoscientific fashion. Other ideas presented here are entirely non-scientific, but have in one way or another impinged on scientific domains or practices.\\
Artificial intelligence is now part of our daily lives, whether in voice recognition systems or route finding apps. But scientists are increasingly drawing on AI to understand society, design new materials and even improve our health.so we can say it play a major role in applied science which is considerd as psedoscience.Stanford researchers are finding new ways to study linguistics, politics, psychology and more based on artificial intelligence. They’re also thinking about how to use AI to improve public policy – and whether, for some tasks, AI really is all its cracked up to be.
 scince applied science is concidered as psedoscience with in it if we consider agriculture as a domain it is possible to use AI to help the farmers in many ways.Artificial intelligence technology is supporting different sectors to boost productivity and efficiency. AI solutions are assisting to overcome the traditional challenges in every field. Likewise. AI in agriculture is helping farmers to improve their efficiency and reduce environmental hostile impacts. The agriculture industry strongly and openly embraced AI into their practice to change the overall outcome. AI is shifting the way our food is produced where the agricultural sector’s emissions have decreased by 20 percent.Adapting AI technology is helping to control and manage any uninvited natural condition.
\end{document}
